---
title: "Analysis"
author: "Prashan A. Welipitiya"
output: pdf_document
---
## This markdown is just an overview of the proccess that I used to get my information. 

```{r, include=FALSE}
#library lists
library(ggplot2)
library(lubridate)
library(dplyr)
```
## Data

I'm going to be pulling the covid numbers from the New York Times Github. They have total numbers of cases and deaths per county and per state. 

```{r}
#https://github.com/nytimes/covid-19-data
setwd("C:/Users/Prashan.Welipitiya/Desktop/covid-19-data")
covid_states = read.csv("us-states.csv")
covid_states$date <- ymd(covid_states$date)
covid_counties = read.csv("us-counties.csv")
covid_counties$date <- ymd(covid_counties$date)

head(covid_counties)
```


I'm going to be using a dataset that was part of a homework assignments in an old class. This dataset has a lot of important information that I am curious about on counties in the US. It includes percent populations of 2016 voting information, elderly, black, white, hispanic, asian, education and income.  

```{r}
county_votes16 <- readRDS(url("https://ericwfox.github.io/data/county_votes16.rds"))
head(county_votes16)
#summary(county_votes16)
```

```{r}
# To match the New York Times data, I'm going to add a collumn that changes the state abbreviation to the name 
county_votes16$state_Name <- state.name[match(county_votes16$state,state.abb)]

# And take the word county out of the county names. 
county_votes16$county_Name <- as.character(county_votes16$county)
county_votes16$county_Name <- substr(county_votes16$county_Name,1,nchar(county_votes16$county_Name) - 7)

head(county_votes16)
```

