---
title: "Analysis"
author: "Prashan A. Welipitiya"
output: pdf_document
---
## This markdown is just an overview of the proccess that I used to get my information. 

```{r, include=FALSE}
#library lists
library(ggplot2)
library(lubridate)
library(dplyr)
```
## Data

I'm going to be pulling the covid numbers from the New York Times Github. They have total numbers of cases and deaths per county and per state. 

```{r}
#https://github.com/nytimes/covid-19-data
setwd("C:/Users/Prashan.Welipitiya/Documents/Prashan/covid-19-data")
covid_states = read.csv("us-states.csv")
covid_states$date <- ymd(covid_states$date)
covid_counties = read.csv("us-counties.csv")
covid_counties$date <- ymd(covid_counties$date)

#head(covid_counties)

td_counties <- covid_counties %>% filter(date == max(covid_counties$date))
head(td_counties)
```


I'm going to be using a dataset that was part of a homework assignments in an old class. This dataset has a lot of important information that I am curious about on counties in the US. It includes percent populations of 2016 voting information, elderly, black, white, hispanic, asian, education and income.  

```{r}
county_votes16 <- readRDS(url("https://ericwfox.github.io/data/county_votes16.rds"))
#head(county_votes16)
```

```{r}
# To match the New York Times data, I'm going to add a collumn that changes the state abbreviation to the name 
county_votes16$state <- state.name[match(county_votes16$state,state.abb)]

# And take the word county out of the county names. 
county_votes16$county <- as.character(county_votes16$county)
county_votes16$county <- substr(county_votes16$county,1,nchar(county_votes16$county) - 7)

head(county_votes16)
```

```{r}
covid = merge(td_counties, county_votes16)
head(covid)
```
I need to add population data. I'm getting this from census.gov (https://www.census.gov/data/datasets/time-series/demo/popest/2010s-counties-total.html#par_textimage_70769902)

```{r}
pop = read.csv('https://www2.census.gov/programs-surveys/popest/datasets/2010-2019/counties/totals/co-est2019-alldata.csv')
```

```{r}
# I just want the county info, state name and population. 
pop19 <- subset(pop, select = c(COUNTY,STNAME,CTYNAME,POPESTIMATE2019))

# County number of 0 is the state population so I'm going to take that out for now. 
popCounty <- pop19 %>% 
  filter(COUNTY != 0)

# Change headers to match

popCounty <- popCounty %>% rename(ID = COUNTY)
popCounty <- popCounty %>% rename(state = STNAME)
popCounty <- popCounty %>% rename(county = CTYNAME)
popCounty <- popCounty %>% rename(popEst19 = POPESTIMATE2019)

# Take the word county out again
popCounty$county <- substr(popCounty$county,1,nchar(popCounty$county) - 7)

head(popCounty)

covid <- merge(popCounty, covid)

```

```{r}
covid$pct_cases <- covid$cases/covid$popEst19
covid$pct_deaths <- covid$deaths/covid$popEst19
head(covid)
```

```{r}
lm1 <- lm(pct_cases~trump_pctvotes + pct_pop65 + pct_black + pct_white + pct_hispanic + pct_asian + highschool + bachelors + income, data = covid)
summary(lm1)
```


```{r}
par(mfrow=c(1,2), cex=0.75) 
plot(lm1, (1:2))
```

